Financial_Analysis

### 2016-07-07 finalwriteup/draft.rmd
write some abstract

>>>>

* Abstracts allow readers to quickly decide whether the research is relevant to their own interests
* get at your main argument quickly
* explain the purpose, goal methods, and results

* why did you do the study?, what is the problem
performing loss-making jobs for fixed fees is a major problem in the consulting, particularly in the competitive construction industry.

* why is it important?
affects the porfitability of a company which impacts the careers, internal morale, and even viability of a company.

* why should someone read your essay?
learn if a company's passively collected data could help them avoid loss making jobs or tactfully enforce strictier contracts.

* what is your main claim?
improve profitability by 9% by avoiding ~4% of projects is a possible way to interpret the agorithm output. other ways are possible.

* discuss variables and your approaches
variables: main employee, % time by each type of employee, team size, client charactersitcs, project characteristics (size, type of work, length)
approaches: complex data with mnay variables, thousands of data points. tried regression as well as machine learning algs: randomf roest and boosted trees, bayesian networks, naive bayes.

* describe evidence to support your claim
hundred of cross validated trials using the 5 methods, as well as 5 blending methods. obtained a 95% confidence interval for each method and simple logistic regression of three models outperformed the others, closely followed by simple averaging. the 95% confidence interval across all cross validated trials was __ to __ profit improvement.

* overview of most important sources

* Results: answer , was hypothesis supported
hypothesis was supprted: CAN improve bottom line of business by mobilising their passively collected data into mL algorhtms.

* implications of your work, meaning
more work to be done on testing the user interface and user ailities further. could assist managers in making better decisions about which projects they should reject or develop a more careful contract structure to improve profits.

### 2016-07-07 financial.rmd
ran individual folds
write some abstract

>>>>

wot <- each.fold(methods = c("log", "rf", "boost"), df.assem = all10mice, x.folds.assem = 5,
                 iterations = 100, seed = 200)

saveRDS(wot, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")

if(.Platform$OS.type == 'windows'){
        ind_folds <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")
} else{
        ind_folds <- readRDS("/Users/yam/Documents/github/consult/finalwriteup/report_data/indiv_folds.rds")
}
```
